Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-17 p2/axioms.tex
Style tweaks
Minor improvements

Finally, we write $A\strext B$ to mean $A\eqext B$ and $A\nequiv B$.
In particular, we write $\wrks{A}$
to mean that $\Dom{A}$ is not empty, that is, if $A$ is defined on some filesystems.
\end{mydef}

@@

\begin{mydef}[Construction and destruction pairs]
A pair of commands on nodes $\pn$ and $n$
is a \emph{construction pair} if the input and output types match
one of the following patterns:
   \begin{align*}
            \cbda{\pn}&\cc  \cbfa{n} \\
            \cbda{\pn}&\cc  \cbda{n} \\
            \cfda{\pn}&\cc  \caaa{\empt}{\valff}{n} \\
            \cfda{\pn}&\cc  \cbda{n}
   \end{align*}
The pair is a \emph{destruction pair} if the types match one of the following:
   \begin{align*}
            \cfba{n}&\cc  \cdba{\pn} \\
            \cfba{n}&\cc  \caaa{\vald}{\valff}{\pn} \\
            \cdba{n}&\cc  \cdba{\pn} \\
            \cdba{n}&\cc  \cdfa{\pn}
   \end{align*}
\end{mydef}

We can see that construction pairs consist of construction commands,
while destruction pairs consist of destruction commands.

\Cref{rules_lemma} summarizes the basic properties of command pairs.
The claims listed are named \emph{\namecrefs{ax_separate_commute}}
as they can also be interpreted as inference rules in a pure
algebraic treatment of filesystem synchronization.
\Cref{sec_algebra} elaborates this approach.
In \cref{axiom_proof} we offer proofs of each of the
\emph{\namecrefs{ax_separate_commute}} based on our model of filesystems.

>>>>

Finally, we write $A\strext B$ to mean $A\eqext B$ and $A\nequiv B$.
In particular, we write $\wrks{A}$
to mean that $\Dom{A}$ is not empty, that is, $A$ is defined on some filesystems.
\end{mydef}

@@

\begin{mydef}[Construction and destruction pairs]
A pair of commands on nodes $\pn$ and $n$
is a \emph{construction pair} if the input and output types match
one of the following patterns:
   \begin{align*}
            \cbda{\pn}&\cc  \cbfa{n} \\
            \cbda{\pn}&\cc  \cbda{n} \\
            \cfda{\pn}&\cc  \caaa{\empt}{\valf}{n} \\
            \cfda{\pn}&\cc  \cbda{n}
   \end{align*}
The pair is a \emph{destruction pair} if the types match one of the following:
   \begin{align*}
            \cfba{n}&\cc  \cdba{\pn} \\
            \cfba{n}&\cc  \caaa{\vald}{\valf}{\pn} \\
            \cdba{n}&\cc  \cdba{\pn} \\
            \cdba{n}&\cc  \cdfa{\pn} \qedhere
   \end{align*}
\end{mydef}
We can see that construction pairs consist of construction commands,
while destruction pairs consist of destruction commands.

\Cref{rules_lemma} summarizes the basic properties of command pairs.
The claims listed are named \emph{\namecrefs{ax_separate_commute}}
as they can also be interpreted as inference rules in a pure
algebraic treatment of filesystem synchronization.
\Cref{sec_algebra} elaborates this approach.

### 2018-07-17 p2/def-commands.tex
Minor improvements

\begin{mydef}[Effect of commands]
The effect of the command $\cxynv$ is defined as follows:
\[
\cxynv\aFS = 
   \begin{cases}
   \fsbroken &\textrm{if $[\FS(n)]\neq[x]$,}\\
   \fsbroken &\textrm{if $\fsreplacement{\FS}{n}{y}$ violates the tree property,}\\
   \fsreplacement{\FS}{n}{y} &\textrm{otherwise.}
   \end{cases}
\]
\end{mydef}
In other words, the command $\cxynv$ breaks a filesystem if the input type $[x]$
does not match the type of the value in the filesystem at $n$, or if after replacing
the value at $n$ with $y$, the resulting filesystem ceases to satisfy the tree property
in \cref{def_treeprop}.

\myskip
There are nine groups of commands considering their input and output types.
Based on these groups we separate commands into four categories 
that reflect their overall effect.
Constructions commands extend the filesystem,
while destruction commands shrink it;
the replacement command replaces a file value with a file value
(which may or may not be different from the original value),
and assertion commands either break the filesystem, or assert the type of the value at a node.
\begin{mydef}[Command categories]\mlabel{def:command_categories}
Depending on their input and output types, filesystem commands
belong to exactly one of the following four categories:
\begin{itemize}
\item[]\emph{Construction commands:}
    $\cbfa{n}$, $\cbda{n}$ and $\cfda{n}$;
\item[]\emph{Destruction commands:}
    $\cdfa{n}$, $\cdba{n}$ and $\cfba{n}$;
\item[]\emph{Assertion commands:}
    $\cbba{n}$ and $\cdda{n}$;
\item[]\emph{Replacement command:}
    $\caaa{\valfx}{\valff}{n}$.
\qedhere
\end{itemize}
\end{mydef}

@@

\myskip
For reasons also listed in \cite{NREC}, in this model we will not consider
a \textit{move (rename)} command.
This turns out to be useful because this would be the only command that affects
filesystems at two nodes at once, therefore describing 
the dependencies for \textit{move} would call for a more complicated model.
As \cref{sec_multidir} details, even with this restriction,
an implementation of the reconciliation algorithm presented here
can still handle \emph{move} commands in its input and output
by splitting them into \emph{delete} and \emph{create} commands,
and merging them later.

>>>>

\begin{mydef}[Effect of commands]
The effect of the command $\cxynv$ is defined as follows:
\[
\cxynv\aFS = 
   \begin{cases}
   \fsbroken &\textrm{if $[\FS(n)]\neq[x]$,}\\
   \fsbroken &\textrm{if $\fsreplacement{\FS}{n}{y}$ violates the tree property,}\\
   \fsreplacement{\FS}{n}{y} &\textrm{otherwise.}
   \end{cases}
\]
\end{mydef}
In other words, the command $\cxynv$ breaks a filesystem if the input type $[x]$
does not match the type of the value in the filesystem at $n$, or if after replacing
the value at $n$ with $y$, the resulting filesystem ceases to satisfy the tree property
as described in \cref{def_treeprop}.

\myskip
There are nine groups of commands considering their input and output types.
Based on these groups we separate commands into four categories 
that reflect their overall effect:
construction commands extend the filesystem,
while destruction commands shrink it;
the replacement command replaces a file value with a file value
(which may or may not be different from the original value),
and assertion commands simply assert the type of the value at a node.
\begin{mydef}[Command categories]\mlabel{def:command_categories}
Depending on their input and output types, filesystem commands
belong to exactly one of the following four categories:
\begin{itemize}
\item[]\emph{Construction commands:}
    $\cbfa{n}$, $\cbda{n}$ and $\cfda{n}$;
\item[]\emph{Destruction commands:}
    $\cdfa{n}$, $\cdba{n}$ and $\cfba{n}$;
\item[]\emph{Assertion commands:}
    $\cbba{n}$ and $\cdda{n}$;
\item[]\emph{Replacement command:}
    $\caaa{\valfx}{\valf}{n}$.
\qedhere
\end{itemize}
\end{mydef}

@@

\myskip
For reasons also listed in \cite{NREC}, in this model we will not consider
a \textit{move (rename)} command.
This turns out to be useful because this would be the only command that affects
filesystems at two nodes at once, therefore describing 
the dependencies for \textit{move} would call for a more complicated model.
As detailed in \cref{sec_multidir}, even with this restriction,
an implementation of the reconciliation algorithm presented here
can still handle \emph{move} commands in its input and output
by splitting them into \emph{delete} and \emph{create} commands,
and merging them later.
